Stats Project 2

### 2022-12-12 article.Rmd
Updates to article.Rmd

---
title: "Stats Project 2"
author: Abhay Sharma | AbhaySh4r.github.io
output:
  pdf_document: default
  html_notebook: default
---
```{r include=FALSE}
library(tidyverse)
library(plotly)
library(car)
library(caret)
library(olsrr)
library(corrplot)
```

@@

\setlength\parindent{18pt}
\section{Introduction}

For this project, we are provided a housing data set from the website Kaggle that contains a large collection of parameters that are likely to be correlated with the Sale Price of their respective houses. Within this data set we find 79 parameters, some of which must ultimately be used to build a predictive model to extrapolate housing prices given a certain set of these parameters.

@@

\subsection{Model Generation and Analysis}
To generate an initial model, we will look at a rudimentary approach to linear regression to see what our data does;

@@

We find that the log-log transform has significantly reduced our residuals and given us a much better fit for the linear regression model, represented by bolstering our R^2 compared to the previous non-transformed model. We can see from the residual plots from the transformed fit that there are a few significantly high leverage/low residual points, and one out outlying point with a very high residual and leverage statistic. We can also verify from the adjusted $R^2$ and RMSE from each model that the transformed model fits the data much better than the a non-transformed model.

@@

For the second analysis in this project,

>>>>

---
title: "Stats Project 2"
author: Abhay Sharma | AbhaySh4r.github.io
output:
  pdf_document: default
  html_notebook: default
---

```{r include=FALSE}
library(tidyverse)
library(plotly)
library(car)
library(caret)
library(olsrr)
library(corrplot)
```

@@

```{=tex}
\setlength\parindent{18pt}
\section{Introduction}
```
For this project, we are provided a housing data set from the website Kaggle that contains a large collection of parameters that are likely to be correlated with the Sale Price of their respective houses. Within this data set we find 79 parameters, some of which must ultimately be used to build a predictive model to extrapolate housing prices given a certain set of these parameters.

@@

\subsection{Model Generation and Analysis}

To generate an initial model, we will look at a rudimentary approach to linear regression to see what our data does;

@@

We find that the log-log transform has significantly reduced our residuals and given us a much better fit for the linear regression model, represented by bolstering our R\^2 compared to the previous non-transformed model. We can see from the residual plots from the transformed fit that there are a few significantly high leverage/low residual points, and one out outlying point with a very high residual and leverage statistic. We can also verify from the adjusted $R^2$ and RMSE from each model that the transformed model fits the data much better than the a non-transformed model.

@@

For the second analysis in this project, we were tasked to generate 4 models using variations of parameters selected by Forward Selection, Backwards Elimination, Stepwise Selection, and a personalized approach. Using these paramters, we can generate Adjusted R\^2 values, CV Press statistics, and finally submit our model to the Kaggle website to obtain a "Kaggle Score" for each model.

To improve the quality of our model, we decided to remove outliers as analaysis shows marginal improvements to R\^2 and marginal deterioration to the Press Statistic. We notice the following outliers:

-   Excessively Expensive \> 700k SalePrice: ID #692 & \# 1183 -

-   Excessively Large \> 100k sq ft.: ID #314, #226, #256, #707

Next, we removed the following highly correlated variables to reduce multicollinearity: LotFrontage, MasVnrArea, GarageYrBlt, OverallQual, TotRmsAbvGrd, GarageCars, TotalBsmtSF, X1stFlrSF, X2ndFlrSF, FullBath. In the correlation matrix, we can see which plots are correlated. After the elimination of the variables mentioned, we see more fairly spare correlated variables.

```{r}
corrplot(cor(t1))
```

## Model Results

| Model                | Adjusted R\^2 | RMSE      | CVPress  |
|----------------------|---------------|-----------|----------|
| Forward Selection    | 0.8333        | 0.1620974 | 43.77074 |
| Backward Elimination | 0.8333        | 0.1620974 | 43.77074 |
| Stepwise Selection   | 0.8333        | 0.1620974 | 43.77074 |

The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20141. While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal. This may indicate that the models are adding/subtracting parameters to result in the exact same parameter list each time. This should be further investigated.
